Empty Homes V1

### 2017-05-29 EmptyHomesV1.Rmd
Leaflet
Attempting to plto with leaflet to make the maps more intereesting. It is proving very difficult.

test2 <- prices %>% left_join(., select(EW2, ECODE, MSOA11CD), 
                              by =c("lsoa11cd"="ECODE")) %>%
  group_by(MSOA11CD) %>%
  summarise(MeanPrice = mean(X2), counts = n()) %>%
  left_join(., IncomeEst, by=c("MSOA11CD"= "MSOA.code")) %>%
  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MeanPrice/Yearly.income)

@@

sum(test2$ratio>6)/nrow(test2)  #about 50% EW
test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>10) %>%
  summarise(total = sum(HighRatio)/n())

@@

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)
SaveFig("LondonCont.png")

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), variable = "LowuseClass", filtermap = FALSE)
SaveFig("LondonDisc.png")

@@

PlotMap(Lambethinfo, AG, title = "Low-use homes in Kensington and Chelsea")

Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")

PlotMap(Chelseainfo, AG, title = "Low-use homes in Kensington and Chelsea")
SaveFig("RBKCLowUse.png")

>>>>

test2 <- prices %>% left_join(., select(EW2, ECODE, MSOA11CD), 
                              by =c("lsoa11cd"="ECODE")) %>%
  group_by(MSOA11CD) %>%
  summarise(MedianPrice = median(X2), counts = n()) %>%
  left_join(., IncomeEst, by=c("MSOA11CD"= "MSOA.code")) %>%
  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MedianPrice/Yearly.income)

@@

sum(test2$ratio>6)/nrow(test2)  #about 50% EW
test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>6) %>%
  summarise(total = sum(HighRatio)/n())

@@

#Chelsea sums
```{r}

sum(Chelseainfo$MeanPrice*Chelseainfo$counts)/sum(Chelseainfo$counts)

prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))

@@

Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
    filter(LAD11NM == "Kensington and Chelsea") %>%
  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")

Chelseainfo %>% 
  filter(LAD11NM == "Kensington and Chelsea") %>%
  group_by(Admin_ward_code) %>%
  mutate(Value = sum(ValLow)/1e6) %>%
  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")
SaveFig("RBKCvalue.png")

Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
    filter(LAD11NM == "Kensington and Chelsea") %>%
PlotMap(., AG, title = "Low-use homes in Kensington and Chelsea")
SaveFig("RBKCLowUse.png")
